Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2016-12-20 paper/structureScene.tex
Edit supervised section

A support vector machine (SVM) is a binary discriminative classifier that attempts to find a separating hyperplane between a pair of classes of that provides the maximal margin between the two sets \cite{Cortes1995}. From another point of view, it attemts to find a direction on which to project in order to maximize separation between two point clouds. Since it is not a generative, but discriminative model, it is able to pick out those feature vectors that best characterize a particular class of auditory scenes compared to another. This property, coupled with its ease of use and efficient implementations \cite{libsvm} have rendered SVMs a popular choice for many classification systems.

@@

Finally, the SVM can also be extended to handle non-linear decision surfaces. This is obtained using the ``kernel trick,'' which exploits the fact that all calculations in the SVM rely only on the inner product between vectors. By replacing this standard inner product by some other positive definite symmetric mapping, such as a Gaussian radial basis function (RBF), this is equivalent to performing a linear SVM after mapping the feature vectors into some high-dimensional space. A non-linear mapping then results in a non-linear decision surface in the orignal space.

>>>>

/ support vector machine (SVM) is a binary discriminative classifier that attempts to find a separating hyperplane between a pair of classes of that provides the maximal margin between the two sets \cite{Cortes1995}. From another point of view, it attempts to find a direction on which to project in order to maximize separation between two point clouds. Since it is not a generative, but discriminative model, it is able to pick out those feature vectors that best characterize a particular class of auditory scenes compared to another. This property, coupled with its ease of use and efficient implementations \cite{libsvm} have rendered SVMs a popular choice for many classification systems.

@@

Finally, the SVM can also be extended to handle non-linear decision surfaces. This is obtained using the ``kernel trick'', which exploits the fact that all calculations in the SVM rely only on the inner product between vectors. By replacing this standard inner product by some other positive definite symmetric mapping, such as a Gaussian radial basis function (RBF), this is equivalent to performing a linear SVM after mapping the feature vectors into some high-dimensional space. A non-linear mapping then results in a non-linear decision surface in the orignal space.
